Modelling the City of Melbourne Pedestrian Data

### 2017-05-07 presentation/proposal_pres.Rmd
corrections made to some errors

```{r, eval = FALSE, tidy = TRUE}
missing_glm <- glm(Hourly_Counts ~ Year * HDay * Time + Month,
                   data = ped_df, family = "poisson")
```

@@

With this project, we want to improve the way we visualise Melbourne's pedestrian activity
```{r, echo = FALSE, fig.retina = 3, out.height="500px", fig.align = 'center'}
ggmap(melbbw) + geom_point(aes(x = Lon, y = Lat, size = Hourly_Counts), colour = "red", alpha = 0.03, data = filter(ped_df, Year == "2016", Month == "March", Time == "9")) + scale_size_area(max_size = 10) + scale_color_distiller(palette = "PuOr") + guides(colour = guide_legend(override.aes = list(alpha = 1))) + theme_light() + labs(x = NULL, y = NULL)
```

@@

```{r, echo = FALSE, message=FALSE, out.height="480px", fig.retina=2, fig.width = 12}
  ggplot(ped_df[ped_df$Sensor_ID == "3", ]) + 
    geom_density(aes(x = Hourly_Counts, colour = Day), adjust = 2, alpha = 0.2) + 
    xlab("Time of the Day") + ylab("Density") + 
    ggtitle(paste("Kernel Density Estimates of Hourly Counts at", ped_loc$`Sensor Description`[ped_loc$`Sensor ID` == "3"], "by Day")) +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom")
```

>>>>

```{r, eval = FALSE}
missing_glm <- glm(Hourly_Counts ~ Year * HDay * Time + Month,
                   data = ped_df, family = "poisson")
```

@@

With this project, we want to improve the way we visualise Melbourne's pedestrian activity
```{r, echo = FALSE, fig.retina = 3, out.height="500px", fig.align = 'center'}
ggmap(melbbw) + geom_point(aes(x = Lon, y = Lat, size = Hourly_Counts), colour = "red", alpha = 0.03, data = filter(ped_df, Year == "2016", Month == "January", Time == "9")) + scale_size_area(max_size = 10) + scale_color_distiller(palette = "PuOr") + guides(colour = guide_legend(override.aes = list(alpha = 1))) + theme_light() + labs(x = NULL, y = NULL)
```

@@

```{r, echo = FALSE, message=FALSE, out.height="480px", fig.retina=2, fig.width = 12}
  ggplot(ped_df[ped_df$Sensor_ID == "3", ]) + 
    geom_density(aes(x = Hourly_Counts, colour = Day), adjust = 2, alpha = 0.2) + 
    xlab("Pedestrian Counts") + ylab("Density") + 
    ggtitle(paste("Kernel Density Estimates of Hourly Counts at", ped_loc$`Sensor Description`[ped_loc$`Sensor ID` == "3"], "by Day")) +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom")
```
